Flat histogram method comparison on 2D Ising Model

### 2020-04-16 ising/ising.tex
made some comments on the ising paper.

@@

\subsection{128 $\times$ 128 Ising system}
For this simulation, we chose a minimum reduced temperature of $1$, which
corresponds to an interesting energy range from $-32768$ to $100$.  The number of
important energy states for this system is $N_S = 8214$.
Fig.~\ref{fig:n128} shows the average error in the entropy as a function of time
for this system with the displacement distance of $\delta_0 = 0.05$. The solid/dashed
lines represent the average of the absolute value of the error in the entropy
averaged over eight simulations using different random number seeds. The range
of average errors for each simulation is shown as a shaded region around its
mean error. By the time $10^{12}$ moves have been made all but the WL and SAD
simulations have begun to converge as $1/\sqrt{t}$. We then see the WL error
saturate around $10^{12}$ moves. The error in the SAD method will continue to
converge faster than $1/\sqrt{t}$ until the update factor approaches that of
1/t-WL at which point both methods will converge equivalently.

\begin{figure}
  \includegraphics[width=\columnwidth]{N128-Cv-error-default.pdf}
  \caption{The error in the heat capacity of the $N=128 \times 128$ after $10^{9}$ moves as calculated with each method.}
  \label{fig:N128-cv-error}
\end{figure}

>>>>

\jpsays{consider adding in minGamma WL here or before 1/t-WL method}

@@

\subsection{128 $\times$ 128 Ising system}
For this simulation, we chose a minimum reduced temperature of $1$, which
corresponds to an interesting energy range from $-32768$ to $100$.  The number of
important energy states for this system is $N_S = 8214$~
\jpsays{This is wrong! This is simulation range. This section needs rewritten.  Why is displacement distance even mentioned?}.
Fig.~\ref{fig:n128} shows the average error in the entropy as a function of time
for this system with the displacement distance of $\delta_0 = 0.05$. The solid/dashed
lines represent the average of the absolute value of the error in the entropy
averaged over eight simulations using different random number seeds. The range
of average errors for each simulation is shown as a shaded region around its
mean error. By the time $10^{12}$ moves have been made all but the WL and SAD
simulations have begun to converge as $1/\sqrt{t}$. We then see the WL error
saturate around $10^{12}$ moves. The error in the SAD method will continue to
converge faster than $1/\sqrt{t}$ until the update factor approaches that of
1/t-WL at which point both methods will converge equivalently.

\begin{figure}
  \includegraphics[width=\columnwidth]{N32-Cv-error-default.pdf}
  \caption{The error in the heat capacity of the $N=32 \times 32$ as calculated with each method.}
  \label{fig:N32-cv-error}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{N128-Cv-error-default.pdf}
  \caption{The error in the heat capacity of the $N=128 \times 128$ as calculated with each method.}
  \label{fig:N128-cv-error}
\end{figure}

\subsection{Separate Heat Capacity Section?}
Why does the heat capacity error saturate (i.e. the error is around 1 out 
but the heat capacity value is much as 1600!)
The smaller system SAD does great and minGamma does great but minGamma needs
the user to pick the right minGamma for the production run otherwise you get
the 128 by 128 results.

We can either break this up or mix in?

Why are we looking at Cv?

(1) the errors in the derivative will be more pronounced. (numerical differentiation of noisy data)

(2) interested in computing thermodynamic quantities

(3) compare with published literature?
